SPARQL on the Open, Decentralised Web

### 2016-08-03 dissertation/related.tex
mention caching in relation to TPF
remove todo

Also, TPF mandates that every response must contain a cardinality
estimate for every triple pattern, an operation that may be quite
expensive for the server.
%TODO: ref characteristic sets?
Indeed, this information may be so expensive to provide that SPARQL
planners may not do so, in order to keep the cost of planning itself
down.

In \cite{verborgh2014querying}, they demonstrated SPARQL evaluation
over TPF, and TPF has become an active area of research.

@@

As such, this mirrors an extensive development known as ``Semantic
Caching'' in the database community. Ahmad et al. \cite{4777801}
surveyed the state of the art in that area. They divided caching
approaches into \emph{page}, \emph{tuple} and \emph{semantic} caches,
and noted that in the two former cases, if only partial results were
available in the cache, the entire result would have to be fetched
from the remote database. Indeed, a page or tuple cache may be used to
cache the results of a whole SPARQL query in HTTP context, but SPARQL
queries are also trivial to partition by e.g. triple patterns or Basic
Graph Patterns, which provides further opportunities for caching where
only partial results are available.\todo{Have I understood this
  correctly? See \url{http://ieeexplore.ieee.org/xpls/icp.jsp?arnumber=1161590\#fig1}}

>>>>

Also, TPF mandates that every response must contain a cardinality
estimate for every triple pattern, an operation that may be quite
expensive for the server.
Indeed, this information may be so expensive to provide that SPARQL
planners may not do so, in order to keep the cost of planning itself
down.

In \cite{verborgh2014querying}, they demonstrated SPARQL evaluation
over TPF, and TPF has become an active area of research. The impact of
caching is also measured in this work, as the result of a single
triple pattern is far easier to cache using HTTP mechanisms than the
result of an entire SPARQL query.

@@

As such, this mirrors an extensive development known as ``Semantic
Caching'' in the database community. Ahmad et al. \cite{4777801}
surveyed the state of the art in that area. They divided caching
approaches into \emph{page}, \emph{tuple} and \emph{semantic} caches,
and noted that in the two former cases, if only partial results were
available in the cache, the entire result would have to be fetched
from the remote database. Indeed, a page or tuple cache may be used to
cache the results of a whole SPARQL query in HTTP context, but SPARQL
queries are also trivial to partition by e.g. triple patterns or Basic
Graph Patterns, which provides further opportunities for caching where
only partial results are available.
